%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author: Vignesh Iyer                                 %
% MS CSE ASU                                           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% -------------- README --------------
% Visit https://github.com/vgnshiyer/ASU-sparkysundevil-resume-template for comprehensive documenation.

% -------------- Resume ---------------
\documentclass{resume}

\begin{document}

% --------- Contact Information -----------
\introduction[
    fullname={Manish Reddy},
    email={manish.botta@protonmail.com},
    phone={909-449-2624},
    linkedin={linkedin.com/in/manish-reddyb/},
    github={github.com/Manishrdy}
]

% --------- Summary -----------
\summary{Software Engineer with 2+ years of experience building scalable web apps and microservices using Python, Node.js, and AWS. Delivered high-impact projects, improving performance and user engagement. Proficient in RESTful APIs, cloud deployments (AWS/Azure), and Agile methodologies. Strong leader with cross-functional collaboration experience, seeking to drive innovation as an SDE.}

% --------- Education ---------
\begin{educationSection}{Education}
    \educationItem[
        university={California State University, San Bernardino, CA},
        graduation={May 2025},
        grade={3.80 GPA},
        program={Master of Science in Computer Science}
    ]
    \educationItem[
        university={Amrita Vishwa Vidyapeetham, Coimbatore, IN},
        graduation={May 2021},
        grade={7.1 CGPA},
        program={Bachelor of Technology in Computer Science and Engineering}
    ]
\end{educationSection}
\vspace{-15pt}
% --------- Skills -----------
\begin{skillsSection}{Technical Skills}
    \skillItem[
        category={Web Technologies},
        skills={C/C++, Networking, Web Application Development, Web Services}
    ] \\
    \skillItem[
        category={Database Management},
        skills={MySQL, MongoDB}
    ] \\
    \skillItem[
        category={Cloud \& DevOps},
        skills={Cloud Platforms, AWS, Microsoft Azure, Google Cloud}
    ] \\
    \skillItem[
        category={Software Fundamentals},
        skills={OS fundamentals, Embedded Development, Linux, QA, Testing, Debugging}
    ]
\end{skillsSection}

% --------- Experience -----------
\begin{experienceSection}{Professional Experience}
    \experienceItem[
        company={Yellow.Ai},
        location={Bengaluru, IN},
        position={Software Engineer},
        duration={Sep 2021 – Jul 2023}
    ]
    \begin{itemize}
    \itemsep -6pt {}
    \item Developed and maintained scalable chatbot applications leveraging NodeJS, Python, and JavaScript, integrating RESTful APIs and secure third-party services (WhatsApp API, Microsoft Teams, Web Portals), with a focus on cloud-based deployment and networking concepts.
    \item Designed backend systems using MySQL and MongoDB, optimizing data storage, retrieval efficiency, and application responsiveness while implementing robust QA and debugging processes.
    \item Integrated Generative AI (OpenAI ChatGPT 3.5/4.0) and NLP techniques (Intent detection, Entities, Sentiment analysis), significantly increasing chatbot accuracy, user engagement (60\% improvement) and customer satisfaction (35\% increase), showcasing proficiency in ML and AI applications.
    \item Performed prompt engineering to fine-tune AI chatbot models, automating repetitive customer interactions, reducing operational overhead, and enhancing user experience through innovative software solutions.
    \item Independently managed delivery of 13 projects during organizational restructuring as the sole retained engineer (8 months experience), while mentoring and evaluating 6 interns to ensure successful outcomes and high-quality deliverables, demonstrating exceptional time management and organizational skills.
    \item Collaborated closely with cross-functional teams (product management, QA, design) following Agile methodologies to iteratively deliver robust chatbot solutions, showcasing strong communication and collaboration abilities.
    \item Proactively collaborated with product managers, QA, and designers, actively participating in Agile ceremonies (sprint planning, retrospectives), demonstrating process-driven approach and ability to streamline existing procedures.
    \end{itemize}

    \experienceItem[
        company={Cognizant},
        location={Coimbatore, In},
        position={Program Trainee Analyst },
        duration={Mar 2021 – Aug 2021}
    ]
    \begin{itemize}
    \itemsep -6pt {}
    \item Designed and developed RESTful APIs using Java Spring Boot, ensuring efficient, secure data communication between client applications and backend services, while implementing microservices architecture.
    \item Implemented microservices architecture, transitioning monolithic applications into lightweight, scalable, and maintainable services, showcasing proficiency in modern software engineering practices.
    \item Built backend logic and database interactions with MySQL and H2 databases, significantly improving application performance and database query efficiency, demonstrating strong problem-solving skills.
    \item Deployed and monitored applications on AWS cloud infrastructure (EC2, S3, CloudWatch) to ensure high availability, scalability, and reliability, gaining hands-on experience with cloud platforms.
    \item Implemented secure JSON payload encryption and decryption using cryptographic packages, adhering to data security and compliance standards, showcasing knowledge in cybersecurity.
    \item Actively participated in Agile/scrum processes, code reviews, debugging, and continuous integration and deployment (CI/CD) workflows, demonstrating strong collaboration and process-oriented approach.
    \end{itemize}

\end{experienceSection}

% --------- Projects -----------
\begin{experienceSection}{Projects}
    \projectItem[
        title={Unity-Based Math Quiz Game for Kids},
        duration={Jan 2024 – May 2024}
    ]
    \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {}
        \item Designed and developed an engaging math quiz game using Unity and Dot-net, incorporating core gameplay mechanics and object-oriented programming principles.
        \item Utilized Agile methodologies (Scrum) for iterative development, conducting comprehensive unit tests, debugging to ensure a stable and responsive gaming experience.
        \item Collaborated with cross-functional teams, leveraging Git for source control management and conducting regular code reviews to maintain high-quality, maintainable code.
        \item Successfully deployed the game on the Amazon App Store, ensuring cross-platform compatibility and robust performance.
    \end{itemize}

    \projectItem[
        title=Text-based Cricket Game Simulation,
        duration=Jun 2023 - Aug 2024
    ]
    \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {}
        \item Designed and implemented a Monte Carlo simulation application in Python to model 20 and 50 over cricket matches, leveraging statistical methods and probabilistic modelling techniques.
        \item Applied advanced algorithmic strategies and object-oriented design principles to ensure efficient, scalable, and maintainable code for simulating complex match dynamics.
        \item Integrated agile methodologies, including continuous integration and unit testing, to iteratively enhance code quality, reliability, and performance under diverse scenarios.
        \item Utilized data-driven insights to fine-tune simulation outcomes, performing rigorous performance profiling and optimization to meet real-time computational demands.
    \end{itemize}
\end{experienceSection}

\end{document}
